Compositional equivalences based on Open pNets\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2019-04-03 2016-Weak-FH-Bisim/WeakBisim.tex
work pn proof of lemma 6 over skype

Moreover, we have for all $p\in[0..n]$:
\begin{mathpar}
Q\models{\openrule
	{
		\gamma_{p j}^{j\in J_p},
		 \Pred_p,  
		\Post_p}
	{\ostate{s_{p i}^{i\in L_Q}} \OTWeakarrow {\alpha_p}
		\ostate{s_{(p+1) i}^{\, i\in L_Q}}}
}		
\end{mathpar}
In the same way,  by Lemma \ref{lem-rel-OT-WOT} we can decompose $\WOT_p$ into  a series of $m'+n'$ tau open transitions and a single observable open transition:
\[Q\models{\openrule
			{
				(\beta^2_j)^{j\in J\cap\Holes(Q)}, {{\Pred'^{2}}},  
				{{\Post'^{2}}}}
				{\ostate{s_{i}^{i\in L_Q}} \OTarrow {\alpha_p}
				\ostate{s_{i}'^{i\in L_Q}}}
				}%\]
\]
We can apply Lemma \ref{lem-compose} on each   $\symb{OT}_p$ of $P$ in the form: 
$P\!\models		
\openrule
    {
       {(\beta^i_p)^{p\in J}},\Pred_p,\Post_p   }
         {\ostate{s^{i\in L}_{pi}} \OTarrow {\alpha} \ostate{s^{i\in L}_{(p+1)i}}}$ 
At the beginning $Q$ is at state $\ostate{s_{q0}}$. We proceed by iteration over the list  $\gamma_{j_0}=[\beta_0..\beta_n]$.\\
For each step when $P$ moves, we have two cases:
\begin{itemize}
\item If $j_0\in J$ then Q moves by one open transition, and by hypothesis  $\beta^i_{j_0}=\beta_t$ with $\beta^i_{j_0}\neq \tau$ for some $t$ such that $t$ has value $0$ at beginning and that is incremented whenever this condition is satisfied. In this case, we have:
\[Q\models{\openrule
	{
		\gamma_{t j}^{j\in J_t},
		 \Pred_t,  
		\Post_t}
	{\ostate{s_{t i}^{i\in L_Q}} \OTWeakarrow {\alpha_t}
		\ostate{s_{(t+1) i}^{\, i\in L_Q}}}
}
\]
By  Lemma \ref{lem-rel-OT-WOT} we can decompose $\WOT_t$ into  a series of $k+k'$ tau open transitions and the observable open transition:

\[Q\models{\openrule
	{
		\gamma_{t j}^{j\in J_t},
		 \Pred_t,  
		\Post_t}
	{\ostate{s_{t i}^{i\in L_Q}} \OTarrow {\alpha_t}
		\ostate{s_{(t+1) i}^{\, i\in L_Q}}}
}
\]
\begin{enumerate}

@@

\item We proceed in the same way for $k'$ last weak open transitions, and we obtain $k'$ open tau transitions.\\
\item For the observable open transition. We have $\alpha_t=\beta_{j_0}$  by Lemma \ref{lem-compose} we obtain:\\ 
\[P[Q]_{j_0}\!\models		
\openrule
    {
       \beta_p^{(p\in J\setminus\{j_0\}) \uplus J_Q},{\Pred_p}\!\!'',{\Post_p}\!\!''   }
         {\ostate{s^{i\in L \uplus L_Q}_{pi}} \OTarrow {\alpha} \ostate{s^{i\in L\uplus L_Q }_{(p+1)i}}}\] \\
 such that  ${\Pred_p}\!\!'' \iff {\Pred_p}
		\land {\Pred_p}\!\!'\land \alpha_t=\beta_{j_0}$, ${\Post_p}\!\!''={\Post_p}\uplus 
		{\Post_p}\!\!'$\\ 
\end{enumerate}

>>>>

Moreover, we have for all $p\in[0..n]$:
\begin{mathpar}
Q\models{\openrule
	{
		\gamma_{p j}^{j\in J_p},
		 \Pred_p,  
		\Post_p}
	{\ostate{s_{p i}^{i\in L_Q}} \OTWeakarrow {\alpha_p}
		\ostate{s_{(p+1) i}^{\, i\in L_Q}}}
}		
\end{mathpar}
In the same way,  by Lemma \ref{lem-rel-OT-WOT} we can decompose $\WOT_p$ into  a series of $m'+n'$ tau open transitions and a single observable open transition:
\[Q\models{\openrule
			{
				(\beta^2_j)^{j\in J\cap\Holes(Q)}, {{\Pred'^{2}}},  
				{{\Post'^{2}}}}
				{\ostate{s_{i}^{i\in L_Q}} \OTarrow {\alpha_p}
				\ostate{s_{i}'^{i\in L_Q}}}
				}%\]
\]

We proceed by iteration on the list of   $\symb{OT}_p$ of $P$ identified above with an additional variable $t$, OTs are of the form: 
$P\!\models		
\openrule
    {
       {(\beta^i_{p j})^{j\in J}},\Pred_p,\Post_p   }
         {\ostate{s^{i\in L}_{pi}} \OTarrow {\alpha} \ostate{s^{i\in L}_{(p+1)i}}}$ 
At the beginning $Q$ is at state $\ostate{s_{0}}$ and $t=0$. 
For each step, we have two cases:
\begin{itemize}
\item If $j_0\in J$ then Q moves by one open transition. By the hypothesis above $\beta^i_{j_0}\neq \tau$. Additionally, we have
$\displaystyle{\gamma_j^{j\in J}=\mybigdotcup_{p=0}^{m_1} \vis{\set{\beta^1_p}} \dotcup  \vis{\set{\beta^2}} \dotcup \mybigdotcup_{p=0}^{m_2} \vis{\set{\beta^3_p}}}$ and\\
 $\gamma_{j_0}=[\beta_0..\beta_n]$, thus
  $\beta^i_{j_0}=\beta_t$ with  for some $t$ such that $t$ has value $0$ at beginning and that is incremented whenever this condition is satisfied.

On the other hand, by hypothesis we have:
\[Q\models{\openrule
	{
		\gamma_{t j}^{j\in J_t},
		 \Pred_t,  
		\Post_t}
	{ \ostate{s_{t}}\OTWeakarrow {\alpha_t}
		\ostate{s_{{(t+1)}}}}
}
\]
By  Lemma \ref{lem-rel-OT-WOT} we can decompose $\WOT_t$ into  a series of $k+k'$ tau open transitions and the observable open transition:

\[Q\models{\openrule
	{
		\gamma_{t j}^{j\in J_t},
		 \Pred_t,  
		\Post_t}
	{\ostate{s^2_{t}}\OTarrow {\alpha_t}
		\ostate{s^3_{t}}}
}
\]
\begin{enumerate}

@@

\item We proceed in the same way for $k'$ last weak open transitions, and we obtain $k'$ open tau transitions.\\
\item For the observable open transition. Because of the definition of $\Pred'$ we can suppose that $\alpha_t=\beta_{j_0}$ \TODO{because else the original WOT does not trigger}. By Lemma \ref{lem-compose} we obtain:\\ 
\[P[Q]_{j_0}\!\models		
\openrule
    {
       \beta_p^{(p\in J\setminus\{j_0\}) \uplus J_Q},{\Pred_p}\!\!'',{\Post_p}\!\!''   }
         {\ostate{s^{i\in L \uplus L_Q}_{pi}} \OTarrow {\alpha} \ostate{s^{i\in L\uplus L_Q }_{(p+1)i}}}\] \\
 such that  ${\Pred_p}\!\!'' \iff {\Pred_p}
		\land {\Pred_p}\!\!'\land \alpha_t=\beta_{j_0}$, ${\Post_p}\!\!''={\Post_p}\uplus 
		{\Post_p}\!\!'$\\ 
\end{enumerate}
